
## Get the Path and select the csv file that will be analysed

```{r}
setwd("G:/Mi unidad/MD/Project 1/Scripts + CSVs")
dd <- read.csv("2 - Knn.csv", sep=";");
```

## Set a color palette for the plots

```{r}
colors = c("#EF5350", "#EC407A", "#AB47BC", "#5C6BC0", "#42A5F5", "#26C6DA", "#26A69A", "#66BB6A", "#D4E157", "#FFEE58", "#FFA726", "#FF7043", "#8D6E63")
```

## Univariate description of age variable

```{r}
# Age
var <- dd$age

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")

```

## Univariate description of job variable

```{r}
# Job
var <- dd$job
barplot(sort(table(var), decreasing = T), col = colors[1]);
pie(table(var), col = colors)
```

## Univariate description of Marital variable

```{r}
# Marital
var <- dd$marital
barplot(sort(table(var), decreasing = T), col = colors[2]);
pie(table(var), col = colors)
```

## Univariate description of education variable

```{r}
# Education
var <- dd$education
barplot(sort(table(var), decreasing = T), col = colors[3]);
pie(table(var), col = colors)
```

## Univariate description of default variable

```{r}
# Default
var <- dd$default
barplot(sort(table(var), decreasing = T), col = colors[4]);
pie(table(var), col = colors)
```

## Univariate description of balance variable

```{r}
var <- dd$balance

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")
```


## Univariate description of housing variable

```{r}
var <- dd$housing
barplot(sort(table(var), decreasing = T), col = colors[5]);
pie(table(var), col = colors)
```

## Univariate description of loan variable

```{r}
var <- dd$loan
barplot(sort(table(var), decreasing = T), col = colors[6]);
pie(table(var), col = colors)
```

## Univariate description of day variable

```{r}

```

## Univariate description of month variable

```{r}

```

## Univariate description of duration variable

```{r}
var <- dd$duration

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")
```

## Univariate description of campaign variable

```{r}
var <- dd$campaign

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")
```

## Univariate description of pdays variable

```{r}
var <- dd$pdays

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")
```

## Univariate description of previous variable

```{r}
var <- dd$previous

cat("Minimum value: ", min(var), "\n")      # Get minimum value
cat("Maximum value: ", max(var), "\n")      # Get maximum value
cat("Mean: ", mean(var), "\n")              # Get mean
cat("Median: ", median(var), "\n")          # Get median
cat("Variance: ", var(var), "\n")           # Get variance
cat("Standard deviation: ", sd(var), "\n")  # Get standard deviation

# Get histogram 
hist(var, xlab = "Age", main = "Histogram of age")

# Get a plot to see if follow a normal distribution
qqnorm(var); qqline(var, col = "red")
```

## Univariate description of potcome variable

```{r}
var <- dd$poutcome
barplot(sort(table(var), decreasing = T), col = colors[7]);
pie(table(var), col = colors)
```

## Univariate description of y variable

```{r}
var <- dd$y
barplot(sort(table(var), decreasing = T), col = colors[1]);
pie(table(var), col = colors)
```


```{r}
summary(dd)
```

